Extended Data

### 2022-03-10 doc/manuscript/Dow_Extended_Data.Rmd
update EDT3 to include March
#124

```{r tree_ring_summary,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
TreeRingResultsSummary <- read.csv("tables_figures/TreeRingResultsSummary.csv",  
                                   stringsAsFactors = FALSE, check.names = FALSE)
TreeRingResultsSummary <- TreeRingResultsSummary[c(2:17)]
kable(TreeRingResultsSummary, 
      caption = tree_ring_summary_caption,  
      col.names = c("species","n","+", "-","+", "-","+", "-","+", "-","+", "-","+", "-","+", "-"), 
      format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" " = 2,  "April" = 2, "May" = 2,"June" = 2,"July" = 2,"Aug" = 2,"April" = 2,"June-July" = 2)) %>%
add_header_above(c(" " = 2,  "univariate analysis" = 10,"multivariate analysis" = 4)) %>%
add_header_above(c(" " = 2,  "n. correlations to monthly mean max. T significant at p=0.05" = 14)) %>%
    column_spec(3:18, width = ".4cm") %>%
pack_rows("Ring-porous", 1, 16, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
pack_rows("Diffuse-porous", 17, 26, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
row_spec(27, bold = T) %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

@@

![**Extended Data Figure 5 | Response of stem growth timing and rates to mean maximum temperatures ($T_{max}$) for the month most closely corresponding to the spring critial temperature window (CTW) for ring- and diffuse-porous speces at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** CTW was defined as the period over which $T_{max}$ was most strongly correlated with the day of year on which 25% of annual growth was achieved ($DOY_{25}$; `r EDT_phenology_parameters`, `r EDF_climwin`), and the most closely corresponding month was determined as that with the greatest number of days within the CTW. Shown are relationships between montlhy $T_{max}$ and days of the year on which 25%, 50%, and 75% total stem growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, respectively; first row); the length of the peak growing season ($L_{pgs}$; second row); maximum growth rate ($g_{max}$; third row); and total seasonal radial stem growth ($\Delta DBH$; fourth row). Posterior predictions of each variable that did not include zero are represented with solid lines, while those that do include zero use dotted lines. 95% credible intervals are represented by bands. For both species groups at both sites, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ declined significantly with April $T_{max}$, with the exception of $DOY_{25}$ for ring-porous species at SCBI. Dots represent growth parameter values for individual tree-year combinations, which were derived by fitting a five-parameter logistic growth model to dendrometer band data.](tables_figures/pheno_Tsensitivity_combo_patchwork_month.png){ width=90% }

>>>>

```{r tree_ring_summary,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
TreeRingResultsSummary <- read.csv("tables_figures/TreeRingResultsSummary.csv",  
                                   stringsAsFactors = FALSE, check.names = FALSE)
TreeRingResultsSummary <- TreeRingResultsSummary[c(2:19)]
kable(TreeRingResultsSummary, 
      caption = tree_ring_summary_caption,  
      col.names = c("species","n","+", "-","+", "-","+", "-","+", "-","+", "-","+", "-","+", "-","+", "-"), 
      format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" " = 2,  "March" =2 , "April" = 2, "May" = 2,"June" = 2,"July" = 2,"Aug" = 2,"April" = 2,"June-July" = 2)) %>%
add_header_above(c(" " = 2,  "univariate analysis" = 12,"multivariate analysis" = 4)) %>%
add_header_above(c(" " = 2,  "n. correlations to monthly mean max. T significant at p=0.05" = 16)) %>%
    column_spec(3:18, width = ".4cm") %>%
pack_rows("Ring-porous", 1, 16, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
pack_rows("Diffuse-porous", 17, 26, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
row_spec(27, bold = T) %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

@@

![**Extended Data Figure 5 | Response of stem growth timing and rates to mean maximum temperatures ($T_{max}$) for the month most closely corresponding to the spring critial temperature window (CTW) for ring- and diffuse-porous speces at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** CTW was defined as the period over which $T_{max}$ was most strongly correlated with the day of year on which 25% of annual growth was achieved ($DOY_{25}$; `r EDT_phenology_parameters`, `r EDF_climwin`), and the most closely corresponding month was determined as that with the greatest number of days within the CTW. Shown are relationships between montlhy $T_{max}$ and days of the year on which 25%, 50%, and 75% total stem growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, respectively; first row); the length of the peak growing season ($L_{pgs}$; second row); maximum growth rate ($g_{max}$; third row); and total seasonal radial stem growth ($\Delta DBH$; fourth row). Posterior predictions of each variable that did not include zero are represented with solid lines, while those that do include zero use dotted lines. 95% credible intervals are represented by bands. For both species groups at both sites, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ declined significantly with April $T_{max}$, with the exception of $DOY_{25}$ for ring-porous species at SCBI. Dots represent growth parameter values for individual tree-year combinations, which were derived by fitting a five-parameter logistic growth model to dendrometer band data.](tables_figures/pheno_Tsensitivity_combo_patchwork_april.png){ width=90% }
